Realistically Interesting Domains for Probabilistic Planners

### 2014-04-09 FinalPaper/paper.tex
Improving domains

To identify unique properties of the domain and identify properties of the
domain that work particularly well for a certain type of planner, we describe
other domains used in the IPPC-11 competition and compare that with the UAV
domain. Since Little and Thi\'ebauw's baseline test for \emph{probabilistic
interestingness} of domains, domains of the IPPC competition have shifted to
those probabilistically interesting domains, which are difficult for
replanners. Often domains that don't pass this test are deemed to be classical
planners in disguise, favoring the use of replanners.

@@

The IPPC-11 domains, Navigation, Traffic, Elevators and SysAdmin are finite-
horizon domains. Navigation, however, is actually a goal oriented domain, if
the goal is reached in the horizon. The method this is defined is that the goal
state is defined as an absorbing state, and there is no reward or cost
associated to staying in the goal state, until the horizon is reached.

@@

>>>>

To identify unique properties of the domain and identify properties of the
domain that work particularly well for a certain type of planner, we describe
other domains used in the IPPC and compare that with the UAV domain. Since
Little and Thi\'ebauw's baseline test for \emph{probabilistic interestingness}
of domains, domains of the IPPC competition have shifted to those
probabilistically interesting domains, which are difficult for replanners.
Often domains that don't pass this test are deemed to be classical planners in
disguise, favoring the use of replanners.

@@

The IPPC-11 domains, Navigation, Traffic, Elevators and SysAdmin are finite-
horizon domains. Navigation, however, is actually a goal oriented domain, if
the goal is reached in the horizon. The method how this is implemented is that
the goal state is defined as an absorbing state, and there is no reward or cost
associated to staying in the goal state, until the horizon is reached.

@@

The domains are constructed such that it will challenge planners to perform
better. This causes that there are issues with the domains when comparing them
with the real world.
